Fragile-X Free-viewing Conversation Eye-tracking Analysis
====

Read in data (not shown).

```{r, echo=FALSE, message=FALSE, warnings=FALSE}  
rm(list=ls())
source("~/Projects/R/Ranalysis/useful.R")
setwd("~/Projects/FreeView/Eyetofacemarks/")
d <- read.csv("Data/aggregate_data_exclusions-7-9.csv")
theme_set(theme_bw())
levels(d$group) <- c("DD","FXS Females","FXS Males")
```

Preliminaries
-----

How many exclusions?

```{r}
sum(d$exclude)
d <- subset(d, exclude==0)
```

Make sure that the data match viola jones preliminary results (sanity check). 

```{r}
qplot(face.after.start.vj, face.dpm, colour=group,label=id,
      geom="text",
      data=d) + 
  ylim(c(0,1)) 
```

Generalized looking at faces
-----

Group-level analysis (all error bars represent 95% confidence interval by non-parametric bootstrap). 

```{r}
ms <- ddply(d, .(group), summarise, 
            face.looking = na.mean(face.dpm),     
            face.cih = ci.high(face.dpm), 
            face.cil = ci.low(face.dpm))

qplot(group,face.looking, geom=c("bar","linerange"),
      fill=group,
      stat="identity",
      ymin=face.looking-face.cil,
      ymax=face.looking+face.cih,
      data=ms) + 
  ylim(c(0,1)) + 
  scale_fill_discrete(name="Participant Group") +  
  ylab("Proportion Looking at Face") + 
  xlab("Participant Group")
```

Now by individuals:

```{r}
qplot(group, face.dpm, data=d, position=position_jitter(.1), col=group) + 
  geom_linerange(aes(x=group, y=face.looking, ymin=face.looking-face.cil,
                     ymax=face.looking+face.cih), col="black", data=ms) + 
  geom_errorbarh(aes(xmin=as.numeric(group)-.05, xmax=as.numeric(group)+.05, 
                     y=face.looking), 
                 data=ms, col="black", height=0, size=2) +
  ylab("Proportion Looking at Face") + 
  xlab("Participant Group")

```

Stickiness analyses
----

Group-level analysis, unsmoothed (1 frame off counts as a break in attention).

```{r}
ms <- ddply(d, .(group), summarise, 
            stickiness = na.mean(stickiness.mean),     
            stickiness.cih = ci.high(stickiness.mean), 
            stickiness.cil = ci.low(stickiness.mean))

qplot(group,stickiness, geom=c("bar","linerange"),
      fill=group, 
      stat="identity",
      ymin=stickiness-stickiness.cil,
      ymax=stickiness+stickiness.cih,
      data=ms) + 
  ylab("Mean Length of Time Looking at Face (s)") + 
  xlab("Participant Group")
```

Now, smoothed (must be 4+ frames off - 133ms at 30hz). Same pattern, but looks are much longer. 

```{r}
ms <- ddply(d, .(group), summarise, 
            stickiness = na.mean(stickiness.sm.mean),     
            stickiness.cih = ci.high(stickiness.sm.mean), 
            stickiness.cil = ci.low(stickiness.sm.mean))

qplot(group,stickiness, geom=c("bar","linerange"),
      fill=group, 
      stat="identity",
      ymin=stickiness-stickiness.cil,
      ymax=stickiness+stickiness.cih,
      data=ms) + 
  ylab("Mean Length of Time Looking at Face (s)") + 
  xlab("Participant Group")
```

Region-level analyses
----

Again, group-level:

```{r}
md <- melt(d, id.var=c("id","group"), 
           measure.var=c("nose","l.eye","r.eye","mouth","l.jaw","r.jaw"))
levels(md$variable) <- c("Nose","L Eye", "R Eye","Mouth","L Jaw","R Jaw")

ms <- ddply(md, .(group,variable), summarise, 
            face.looking = na.mean(value), 
            face.cih = ci.high(value), 
            face.cil = ci.low(value))

qplot(variable,face.looking, geom=c("bar","linerange"),
      facets=. ~ group, fill=variable,
      stat="identity",
      position=position_dodge(width=.9),
      ymin=face.looking-face.cil,
      ymax=face.looking+face.cih,
      data=ms) + 
  ylim(c(0,.3)) + 
  ylab("Proportion Looking") + 
  xlab("Region") + 
  scale_fill_discrete(name="Region") + 
  theme(axis.text.x = element_text(angle = 90, vjust=.5, hjust = 1)) 
```

Showing individuals:

```{r}
qplot(variable, value, data=md, position=position_jitter(.1), col=variable, 
      facets=.~ group) + 
  geom_linerange(aes(x=variable, y=face.looking, ymin=face.looking-face.cil,
                     ymax=face.looking+face.cih), col="black", data=ms) + 
  geom_errorbarh(aes(xmin=as.numeric(variable)-.25, xmax=as.numeric(variable)+.25, 
                     y=face.looking), col="black",
                 data=ms, height=0, size=2) + 
  ylab("Proportion Looking") + 
  xlab("Region") + 
  scale_fill_discrete(name="Region") + 
  theme(axis.text.x = element_text(angle = 90, vjust=.5, hjust = 1)) 
```

That's a little messy, so let's try boxplots:

```{r}
qplot(variable, value, data=md,  col=variable,
      geom="boxplot",adjust=1,
      facets=.~ group)+ 
  ylab("Proportion Looking") + 
  xlab("Region") + 
  scale_fill_discrete(name="Region") + 
  theme(axis.text.x = element_text(angle = 90, vjust=.5, hjust = 1)) 
```

Demographic variables
----

Plot face looking by age:

```{r}
qplot(age, face.dpm, colour=group, data=d) + 
  geom_smooth(method="lm", se=FALSE) + 
  xlab("Age (years)") + 
  ylab("Proportion Face Looking") + 
  scale_colour_discrete(name="Participant Group")
```

IQ:

```{r}
qplot(iq, face.dpm, colour=group, data=d) + 
  geom_smooth(method="lm", se=FALSE)+ 
  xlab("IQ (standardized)") + 
  ylab("Proportion Face Looking") + 
  scale_colour_discrete(name="Participant Group")
```

Statistical models
----

Clearly there's a strong face looking by group effect:

```{r}
l <- lm(face.dpm ~ group, data=d)
summary(l)
anova(l)
```

Now look at age effects. No interaction, but main effects of age and group.

```{r}
l.age <- lm(face.dpm ~ iq * group, data=d)
summary(l.age)
anova(l.age)
```

Now look at IQ. Same story.

```{r}
l.iq <- lm(face.dpm ~ iq * group, data=d)
summary(l.iq)
anova(l.iq)
```

Time-course analyses
----

Read in data, first. 

```{r}
tc <- data.frame()
fs <- dir("Data/timecourse",pattern="*.csv")

for (f in fs) {
  s <- read.csv(paste("Data/timecourse/",f,sep=""))
  s <- s[-c(1,2),] ## remove the first two rows, IQ and age 
  tc <- rbind.fill(tc, 
                   data.frame(id=as.numeric(strsplit(f,"\\.")[[1]][2]),
                              t=1:length(s),
                              region=s))
  
  }

tc$face <- tc$region != 0
tc$t.sec <- tc$t / 5 # 5 hz downsampling

head(tc)
```

Now aggregate this over time. First a sanity check to make sure we're coming up with the DPM data. As you can see, this does in fact recover the correct mapping.

```{r}
head(tc)

ms <- ddply(tc, .(id), summarise, face = mean(face,na.rm=TRUE))
dm <- merge(d,ms)
qplot(face.dpm, face, data=dm)
```

Now figure out the timing. I believe we are at 60hz.

```{r}
ms <-  ddply(tc, .(id), summarise, t.sec = max(t.sec)/60)
qplot(t.sec, data=ms) + 
  xlab("Session length (min)")

d <- merge(d, ms)
```

Now compute timecourses. 

```{r, cache=TRUE}
tc <- merge(tc, d[,c("id","group")]) # merge in group labels
tc$t.bin <- floor(tc$t.sec/10)*10 # break into 10s bins
tcs <- ddply(tc, .(t.bin,group), summarise,
             face.mean = mean(face), 
             face.cil = ci.low(face),
             face.cih = ci.high(face))
             
qplot(t.bin/60, face.mean, 
      ymin=face.mean - face.cil,
      ymax=face.mean + face.cih,
      geom="pointrange",
      col=group, data=tcs) + 
  xlim(c(0,10)) + 
  ylim(c(0,.8)) +
  xlab("Time (min)") + 
  ylab("Proportion Face Looking") +
  geom_smooth()
```

Write output.

```{r}
write.csv(d,"Data/output.csv",row.names=FALSE)
```
